---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# populi: Utilities and Tools in R to Extract, Process, and Structure Population Datasets from the World Population Prospects of the United Nations Department of Economic and Social Affairs

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The Population Division of the Department of Economic and Social Affairs of the United Nations Secretariat prepares regular revisions of the World Population Prospects - the official United Nations population estimates and projections. This package provides utilities and tools to extract, process, and structure these population datasets for use in R.

## Installation

<!--
You can install the released version of populi from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("populi")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rapidsurveys/populi")
```
-->

You can install the development version of `populi` from [GitHub](https://github.com/populi) with:

```{r install, echo = TRUE, eval = FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("rapidsurveys/populi")
```
